### 2021-02-24 Chapter-1/Chapter-1.tex

\section{Dissertation Organization}
The rest of the dissertation is organized as follows. We present relevant backgrounds and related works in Chapter~\ref{chapter2}. Chapter~\ref{chapter3} presents a novel method to detect side-channel vulnerabilities in binary executables. Chapter~\ref{chapter4} present a method that can quantify each side-channel leakage in a single trace attack. Chapter~\ref{chapter5} extend the approach and quantifies the side-channel leakage in chosen message attacks. Chapter~\ref{chapter6} conclude the thesis.

>>>>

\section{Dissertation Organization}
The rest of the dissertation is organized as follows. We present relevant backgrounds and related works in Chapter~\ref{chapter2}. Chapter~\ref{chapter3} presents a novel method to detect side-channel vulnerabilities in binary executables. Chapter~\ref{chapter4} presents a method that can quantify each side-channel leakage in a single trace attack. Chapter~\ref{chapter5} extends the approach and quantifies the side-channel leakage in chosen message attacks. Chapter~\ref{chapter6} concludes the thesis.
